Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
add references; minor discussion changes

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (Tab.~\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
and their spatial layout at their first occurence in a movie.
% cut to recurrent scene
On revisiting an already established setting later in the movie, the field sizes
of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
more often depict people talking to each other, or objects that are relevant to
the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
mercado2011filmmakers}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro

@@

@@

% previous studies
Several studies have reported increased hemodynamic activity in the PPA,
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
However, reports regarding the correlates of processing spatial information in
non-visual stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing spatial information, we
employed a naturalistic movie stimulus that was designed for entertainment.

% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content
of individual movie frames (color, faces, language, and human bodies) and found
that the expected specialization of functional areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the stimulus
structure, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and only later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
We hypothesized that due to the complex nature of a naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information availability in particular events accessible to
convential model-based statistical analysis of BOLD fMRI data.
%
This approach required a detailed description of the occurence of relevant
stimulus features. For both types of naturalistic stimuli used here, a movie
and its audio-description, this annotation revealed the respective number of
incidentally occurring events to be similar to those of a conventional
experimental paradigm used in neuroimaging, for the purpose of localizing
particular regions of interest.

% group AV
On a group-average level, results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
conventionally localized PPA, but also extending into earlier visual cortices.
% group AD
Likewise, results for the audio-description identify significant activation in the PPA
but restricted to its anterior part.
% individual level
Moroever, the group averages are representative for the majority of individual
results, where, for example, the audio-description stimulus yields
bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
in one participant.
% meaning: generalization to naturalistic stimuli
These findings suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie or a purely auditory narrative.
% narrative as substitute
The presented evidence on the in-principle suitability of an auditory-only paradigm
for localizing the PPA, may offer a path to the development of diagnostic procedures
more suitable for populations of individuals with visual impairments or conditions
like nystagmus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.\todo{what is the other evidence?}

@@

% hypothesis
Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
information embedded in the audio-description stimulus would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\cite{aziz2008modulation} modeled events from onset to offset of sentences,
describing unknown and famous places and faces, and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Their results showed decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places in contrast
to famous faces.
% we: model & whole brain
In this study, we modeled events from onset to offset of single words and performed a
voxelwise whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \cite{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

% previous studies: no task
It is common for conventional localizer paradigms to
employ a task to keep participants attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
% but still: we are different
This naturalistic paradigm nevertheless differs from \cite{epstein1998ppa},
because the relevant stimulus features were embedded in a continuous stream of complex
auditory (and visual) information that makes it unlikely that participants
speculate on the purpose of the investigation or perform undesired and unknown
evaluation or categorization of isolated stimuli.
% concluding statement: kinda automatic process
Our results therefore indicate that verbally communicated spatial information
is processed, in the anterior PPA, automatically and without specifically
guided attention.

@@

% optimal stimulus type in vision
In the visual domain, pictures of landscapes and not pictures of landmarks or
buildings are considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
In the audio-description's primary contrast, we did not include the categories
that contained switches from one setting to another (\texttt{se\_new} and
\texttt{se\_old}) which one might assume to contain the auditory equivalent to
pictures of landscapes.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% visual system => gist in milliseconds
Humans can identify the gist of a rich visual scene within the duration of a
single fixation \citep{henderson2003human}.
%
Hence, further studies might investigate if vague verbal descriptions of
landscapes lead to a different hemodynamic activity level than descriptions of
more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').

% AD annotation > AV annotation
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 participants and a unilateral right ROI in two participants (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$t$-threshold in $t$-map from one of three contrasts by visual judgment, we used
the same contrast and threshold ($Z$>3.4, $p$<.05 cluster-corrected) for all
participants.
% in the current study
The audio-description yielded significant bilateral clusters in 9 of 14 participants
(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
significant cluster in one participant.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but a reliable pattern across results of
individual study participants.
% concluding statement
Further, our exploratory analysis suggests that a naturalistic auditory stimulus
can, in principle, be applied to localize (the anterior part) of a higher-level
visual area in the majority of participants.
% one threshold (and contrast) to rule them all
Nevertheless, further studies that aim for individual diagnostics / ROI
localization should inspect more than one contrast, and use an individual
threshold or a sphere around the local maximum \citep{poldrack2007region} in the
parahippocampal region.

@@

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual compared to the verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Contrary, the aPPA is functionally more responsive than the pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Contrary, the aPPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to a hypothesis by \citep{baldassano2013differential} the PPA consists
of subregions that process different aspects of a visual scene and cooperate to
build a complete scene representation.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent in both visual and
verbal stimuli.

>>>>

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (Tab.~\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
and their spatial layout at their first occurence in a movie.
% cut to recurrent scene
On revisiting an already established setting later in the movie, the field sizes
of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
more often depict people talking to each other, or objects that are relevant to
the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
katz1991film, mascelli1998five}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro

@@

\pagebreak [4]

@@

% previous studies
Several studies have reported increased hemodynamic activity in the PPA,
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
However, reports regarding the correlates of processing spatial information in
auditory semantic stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing spatial information, we
employed a naturalistic movie stimulus that was designed for entertainment.

% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content
of individual movie frames (color, faces, language, and human bodies) and found
that the expected specialization of functional areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the stimulus
structure, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography,
katz1991film, mascelli1998five}.
% hypo
We\todo{following two sentences are confusing imo} hypothesized that due to the complex nature of a naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information availability in particular events accessible to
convential model-based statistical analysis of BOLD fMRI data.
%
This approach required a detailed description of the occurence of relevant
stimulus features. For both types of naturalistic stimuli used here, a movie
and its audio-description, this annotation revealed the respective number of
incidentally occurring events to be similar to those of a conventional
experimental paradigm used in neuroimaging, for the purpose of localizing
particular regions of interest.

% group AV
On a group-average level, results for the audio-visual movie show significantly
increased hemodynamic activity spatially overlapping with a conventionally
localized PPA, but also extending into earlier visual cortices.
% group AD
Likewise, results for the audio-description identify significant activation in
the PPA but restricted to its anterior part.
% individual level
Moroever, the group averages are representative for the majority of individual
results, where, for example, the audio-description stimulus yields bilateral
clusters in the anterior PPA of nine participants and a unilateral cluster in
one participant.
% meaning: generalization to naturalistic stimuli
These findings suggest that increased activation in the PPA during the
perception of static pictures generalizes to the perception of spatial
information embedded in a movie or a purely auditory narrative.
% narrative as substitute
The presented evidence on the in-principle suitability of an auditory-only
paradigm for localizing the PPA may offer a path to the development of
diagnostic procedures more suitable for populations of individuals with visual
impairments or conditions like nystagmus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions \citep{aminoff2007parahippocampal, aminoff2015associative,
baldassano2013differential, baldassano2016two, baumann2016functional}.

@@

% hypothesis
Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
information embedded in the audio-description would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\cite{aziz2008modulation} modeled events from onset to offset of sentences,
describing unknown and famous places and faces, and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Their results showed decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places in contrast
to famous faces.
% we: model & whole brain
In the current study, we modeled events from onset to offset of single words and performed a
voxelwise whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \cite{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

% previous studies: no task
It is common for conventional localizer paradigms to
employ a task to keep participants attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
% but still: we are different
This naturalistic paradigm nevertheless differs from \cite{epstein1998ppa},
because the relevant stimulus features were embedded in a continuous stream of complex
auditory (and visual) information which makes it unlikely that participants
speculated on the purpose of the investigation or perform undesired and unknown
evaluation or categorization of isolated stimuli.
% concluding statement: kinda automatic process
Our results therefore indicate that verbally communicated spatial information
is processed, in the anterior PPA, automatically and without specifically
guided attention.

@@

% optimal stimulus type in vision
In the visual domain, pictures of landscapes and not pictures of landmarks or
buildings are considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
In the audio-description's primary contrast, we did not include the categories
that contain switches from one setting to another (\texttt{se\_new} and
\texttt{se\_old}) which one might assume to contain the auditory equivalent to
pictures of landscapes.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% visual system => gist in milliseconds
Humans can identify the gist of a rich visual scene within the duration of a
single fixation \citep{henderson2003human}.
%
Hence, further studies might investigate if vague verbal descriptions of
landscapes lead to a different hemodynamic activity level than descriptions of
more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').

% AD annotation > AV annotation
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 participants and a unilateral right ROI in two participants (sub-04, sub-20).
%
Whereas \cite{sengupta2016extension} chose the subjectively ``best fitting''
$t$-threshold in a $t$-map from one of three contrasts by visual judgment, we used
the same contrast and threshold ($Z$>3.4, $p$<.05 cluster-corrected) for all
participants.
% in the current study
The audio-description yielded significant bilateral clusters in 9 of 14 participants
(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
significant cluster in one participant.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but a reliable pattern across results of
individual study participants.
% concluding statement
Further, our exploratory analysis suggests that a naturalistic auditory stimulus
can, in principle, be applied to localize (the anterior part) of a higher-level
visual area in the majority of participants.
% one threshold (and contrast) to rule them all
Nevertheless, further studies that aim for individual diagnostics / ROI
localization should inspect more than one contrast, and use an individual
threshold or a sphere around the local maximum \citep{poldrack2007region} in the
parahippocampal region.

@@

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual stimuli compared to the purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Contrary, the aPPA is functionally more responsive than the pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal, aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Contrary, the aPPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to a hypothesis by \citep{baldassano2013differential} the PPA consists
of subregions that process different aspects of a visual scene and cooperate to
build a complete scene representation.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as immanent in both visual and
verbal stimuli.
